---
title: "Architecture design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Architecture design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
### Architecture overview {-}
The tacrolimuskws package provides a clinical decision support system (CDS) for tacrolimus dose adaptation of de novo kidney transplant recipients in the first 14 days post-transplant.

The CDS can be accessed by the KWS EHR through a Plumber API. This component stores any received requests in a KWS-format Mongo database, and then translates them into a generic format that can be used by tdmore. The dose recommendation is obtained and stored in a separate tdmore-format Mongo database, and the resulting recommendation is then sent back to the KWS system.
The Plumber API also provides an admin interface to get an overview of all received requests and responses.

The CDS can be accessed by physicians through a Shiny web interface. The web interface consults the tdmore-format Mongo database and displays the input/output information.


```{r architecture, echo=FALSE}
DiagrammeR::grViz("
digraph G {
	KWS -> Plumber;
	Plumber -> MongoKWSDb;
	Plumber -> translate;
	translate -> tdmore;
	tdmore -> translate;
	translate -> Plumber;
	Plumber -> KWS;
	MongoKWSDb -> PlumberAdmin;
	
	translate -> TdmoreDb;
	TdmoreDb -> tdmoreshiny;
	tdmoreshiny -> Shiny;
	Shiny -> Physician;
}
")
```

### Plumber API
The KWS sends requests using a specific format. This request is translated into model-specific dataframes.




### Code appendix
```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```
